<!--{{dataset:FarmInventory}}-->

```{r context="server-start"}
##When the student begins a tutorial or hits "start over" this will reset their homework information. This will clear their
## homework grade and any homework problems submissions currently stored.
event_register_handler("session_start", function(session, event, data) {
  hmw_info <<- reactiveValues(s_id = get_tutorial_info()$user_id, #Student's id. Uses their currently running account's username, which if its the campus RStudio Online server will be their student username
                           tutorial_name = "Filter", #The name of the tutorial
                           hmw_grade = 0, # The number of homework questions they have answer correctly 
                           submissions = list( # A list for tracking the information on all of the student's homework problem submissions
                               hmw1 = list(type="questionaire", 
                                           q_text="(True or False), filter() modifies the dataframe passed to it.",
                                           choices=c("True", "False"), 
                                           is_correct = FALSE, 
                                           submitted_answer = "",
                                           error_msg = ""),
                               hmw2 = list(type="questionaire", 
                                           q_text="The & operator only evaulates to true if :",
                                           choices=c("both conditions are true", "neither condition is true", 
                                                     "either condition is true", "both conditions are false", "None of the above"), 
                                           is_correct = FALSE, 
                                           submitted_answer = "",
                                           error_msg = ""),
                               hmw3 = list(type="code", 
                                           q_text="Fill in the blanks with the necessary code so that only the vegetables from Bailey Farm are listed. ", 
                                           choices="filter(data, ____ == \"Peppridge\" ____ type ____ \"VEGETABLE\")",
                                           is_correct = FALSE, 
                                           submitted_answer = "",
                                           error_msg = ""),
                               hmw4 = list(type="code", 
                                           q_text="Debugging Exercise - Fix the following piece of code so that only the dairy products are listed.", 
                                           choices="filter(farm_data, type = \"dairy\")", 
                                           is_correct = FALSE, 
                                           submitted_answer = "",
                                           error_msg = ""),
                               hmw5 = list(type="code", 
                                           q_text="Write the necessary code to list all of the legumes that have an average shelf life of at least 30 days.", 
                                           choices=NULL, 
                                           is_correct = FALSE, 
                                           submitted_answer = "",
                                           error_msg = ""),
                               hmw6 = list(type="code", 
                                           q_text="Write the necessary code to list all of the Russian Blue Potatoes and Purple Sweet Potatoes that have over 2,000 pounds in stock.", 
                                           choices=NULL, 
                                           is_correct = FALSE, 
                                           submitted_answer = "",
                                           error_msg = "")))

})


```

```{r prepare-hmw-filter-1, echo=FALSE}
farm_data <- read_csv("data/hmw_data.csv", col_types="ccddffi");
```

```{r, echo=FALSE}
#Prepare local copy of data directory
farm_data <- read_csv("data/hmw_data.csv", col_types="ccddffi");
```

```{r}
head(farm_data)
```

#### Problem 1 

```{r filter_hmw1, echo=FALSE}

question("(True or False), filter() modifies the dataframe passed to it.",
  answer("True"),
  answer("False", correct=TRUE),
  incorrect = "Incorrect, as stated [here](https://r4ds.had.co.nz/transform.html?q=filter#filter-rows-with-filter), filter() does not modify the data passed to it. filter() instead creates and returns a new dataframe.",
  allow_retry = TRUE
)
```

#### Problem 2 
```{r filter_hmw2, echo=FALSE, exercise.startover = TRUE}
  question("The & operator only evaulates to true if :",
  answer("both conditions are true", correct = TRUE),
  answer("neither condition is true"),
  answer("either condition is true"),
  answer("both conditions are false"),
  answer("None of the above"),
  allow_retry = TRUE
)
```

#### Problem 3 
Fill in the blanks with the necessary code so that only the vegetables from Bailey Farm are listed.

```{r filter_hmw3, exercise = TRUE, exercise.blanks = "___+", exercise.completion = FALSE, exercise.setup = "prepare-hmw-filter-1"}
filter(farm_data, ____ == "Peppridge" ____ type ____ "VEGETABLE")
```

```{r filter_hmw3-check}
grade_result(
  pass_if(~identical(.result, filter(farm_data, f_name == "Peppridge" & type == "VEGETABLE")))
)
```

#### Problem 4 
Debugging Exercise - Fix the following piece of code so that only the dairy products are listed.
```{r filter_hmw4, exercise = TRUE, exercise.completion = FALSE, , exercise.setup = "prepare-hmw-filter-1"}
filter(farm_data, type = "dairy")
```

```{r filter_hmw4-check}
grade_result(
  pass_if(~identical(.result, filter(farm_data, type == "DAIRY")))
)
```

#### Problem 5
Write the necessary code to list all of the legumes that have an average shelf life of at least 30 days.
```{r filter_hmw5, exercise = TRUE, exercise.completion = FALSE, exercise.setup = "prepare-hmw-filter-1"}

```  

```{r filter_hmw5-check}
grade_result(
  pass_if(~identical(.result, filter(farm_data, type == "LEGUME", avg_sl >= 30)))
)
```

#### Problem 6
Write the necessary code to list all of the Russian Blue Potatoes and Purple Sweet Potatoes that have over 2,000 pounds in stock.
```{r filter_hmw6, exercise = TRUE, exercise.completion = FALSE, exercise.setup = "prepare-hmw-filter-1"}

```

```{r filter_hmw6-check}
grade_result(
  pass_if(~identical(.result, filter(farm_data, p_name == "Russian Blue Potato" | p_name == "Purple Sweet Potato",  q_in_lbs > 2000)))
)
```

