<!--{{dataset:GreenVehicles}}-->

```{r context="server-start"}
##When the student begins a tutorial or hits "start over" this will reset their homework information. This will clear their
## homework grade and any homework problems submissions currently stored.
event_register_handler("session_start", function(session, event, data) {
  print("Session: ")
  print(session)
  hmw_info <<- reactiveValues(s_id = get_tutorial_info()$user_id, 
                           tutorial_name = "Select",# The name of the tutorial
                           hmw_grade = 0.0, 
                           submissions = list(
                                  hmw1 = list(type="questionaire", 
                                               q_text="When using select(), any columns that are not listed will be :",
                                               choices=c("left out of the returned data frame", "deleted from the provided data frame", "placed at the end of the returned data frame", "None of the above"), 
                                               is_correct = FALSE, 
                                               submitted_answer = "",
                                               error_msg = ""),
                                  hmw2 = list(type="questionaire", 
                                               q_text=" After importing an online baseball dataset, you notice one of the variables is named \"# of Home Runs\". How could you rename this variable so it follows proper naming conventions? :",
                                               choices=c("select(bball, n_home_runs = \"# of Home Runs\")", "select(bbal, #_home_runs = \"# of Home Runs\")", "select(bbal, HomeRunsCount = \"# of Home Runs\")", "None of the above"), 
                                               is_correct = FALSE, 
                                               submitted_answer = "",
                                               error_msg = ""),
                                  hmw3 = list(type="code", 
                                               q_text="Fill in the blanks with the necessary code so that only the car's model, year, and smartway status are listed.", 
                                               choices="select(green_vehicles, _____, _____, _____)",
                                               is_correct = FALSE, 
                                               submitted_answer = "",
                                               error_msg = ""),
                                  hmw4 = list(type="code", 
                                               q_text="Debugging Exercise - Fix the following piece of code so that it is able to run correctly.", 
                                               choices="select(green_vehicles, 1;5, c1ty_mpg, greenhouse_gas_score = gg_score)",
                                               is_correct = FALSE, 
                                               submitted_answer = "",
                                               error_msg = ""),
                                  hmw5 = list(type="code", 
                                               q_text="Write the necessary code so that the car's fuel type, vehicle class, combined mpg, and air pollution score are listed. Also, rename the air pollution score variable as **ap_score**", 
                                               choices=NULL,
                                               is_correct = FALSE, 
                                               submitted_answer = "",
                                               error_msg = ""),
                                  hmw6 = list(type="code", 
                                               q_text="Write the necessary code to organize each car's information as follows: the year to the transmission type, the car's 3 mpg scores, the air pollution score, and its smartway status. (Variable renaming is not required for this exercise)", 
                                               choices=NULL,
                                               is_correct = FALSE, 
                                               submitted_answer = "",
                                               error_msg = "")
                                   ))
})
```


#### Problem 1
```{r select_hmw1, echo=FALSE, exercise.startover = TRUE}
  question("When using select(), any columns that are not listed will be :",
  answer("left out of the returned data frame", correct = TRUE),
  answer("deleted from the provided data frame", message="Incorrect: select(), like all of the dplyr functions, never modifies the provided data frame."),
  answer("placed at the end of the returned data frame", message="Incorrect: select() will not return any columns you did not explicitly ask for."),
  answer("None of the above"),
  random_answer_order = TRUE,
  allow_retry = TRUE
)
```

#### Problem 2
```{r select_hmw2, echo=FALSE, exercise.startover = TRUE}
  question("After importing an online baseball dataset, you notice one of the variables is named \"# of Home Runs\". How could you rename this variable so it follows proper naming conventions?",
  answer("select(bball, n_home_runs = \"# of Home Runs\")", correct = TRUE),
  answer("select(bbal, #_home_runs = \"# of Home Runs\")", message="Incorrect: Variable names must start with a letter. Also, the pound sign (#) in R represents a comment, so this will actually *comment out* the rest of the select statement."),
  answer("select(bbal, HomeRunsCount = \"# of Home Runs\")", message="Incorrect: While this is valid syntax, our naming convention requires variables to be lowercase, noun phrases, and use under_scores."),
  answer("None of the above"),
  random_answer_order = TRUE,
  allow_retry = TRUE
)
```
#### Problem 3 
Fill in the blanks with the necessary code so that only the car's model, year, and smartway status are listed.
```{r select_hmw3, exercise = TRUE, exercise.blanks = "___+", exercise.completion = FALSE}
select(green_vehicles, _____, _____, _____)
```

```{r select_hmw3-check}
grade_result(
  pass_if(~identical(.result, select(green_vehicles, model, year, smartway)))#Replace TRUE with the solution's code
)
```


#### Problem 4
Debugging Exercise - Fix the following piece of code so that it can run correctly.
```{r select_hmw4, exercise = TRUE, exercise.completion = FALSE}
select(green_vehicles, 1;5, c1ty_mpg, greenhouse_gas_score = gg_score) 
```  

<div id="select_hmw4-hint">
**Hint:** There are three errors you will need to locate and fix.
</div>

```{r select_hmw4-check}
grade_result(
  pass_if(~identical(.result, select(green_vehicles, 1:5, city_mpg, gg_score = greenhouse_gas_score)))#Replace TRUE with the solution's code
)
```

#### Problem 5 
Write the necessary code so that the car's fuel type, vehicle class, combined mpg, and air pollution score are listed. Also, rename the air pollution score variable as **ap_score**.
```{r select_hmw5, exercise = TRUE, exercise.completion = FALSE}

```

```{r select_hmw5-check}
grade_result(
  pass_if(~identical(.result, select(green_vehicles, fuel, veh_class, cmb_mpg, ap_score = air_pollution_score)))#Replace TRUE with the solution's code
)
```

#### Problem 6 
Write the necessary code to organize each car's information as follows: the year to the transmission type, the car's 3 mpg scores, the air pollution score, and its smartway status. (Variable renaming is not required for this exercise)
```{r select_hmw6, exercise = TRUE, exercise.completion = FALSE}

```

```{r select_hmw6-check}
grade_result(
  pass_if(~identical(.result, select(green_vehicles, 1:6, city_mpg:cmb_mpg, air_pollution_score, smartway)))#Replace TRUE with the solution's code
)
```
